Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-11-07 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Add missing information to references in bibliography

\bibitem[{\itshape Benzm\"uller \& Weber \& Woltzenlogel Paleo(2016)}]{controversy}
Benzm\"uller, C. \& Weber, L. \& Woltzenlogel Paleo, B. 2016. {\itshape Computer-Assisted Analysis of the Anderson-H\'ajek Ontological Controversy}. In: {\itshape Logica Universalis} 10 (2016)

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2013a)}]{IWIL}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2013a. {\itshape G{\"{o}}del's God on the Computer}. Proceedings of the 10th International Workshop on the Implementation of Logics. pp. 1--2.

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015b)}]{ReasoningWebSummerSchool}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015b. {\itshape Higher-Order Modal Logics: Automation and Applications}. Reasoning Web. Web Logic Rules - 11th International Summer School 2015. Tutorial Lectures. Lecture Notes in Computer Science. Springer. pp. 32--74.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015c)}]{SpiritualQuest}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015c. {\itshape Experiments in Computational Metaphysics: G\"odel's Proof of God's Existence}. Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest. vol. 9. pp. 23--40.

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016b)}]{ModalCollapse}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016b. {\itshape The Modal Collapse as a Collapse of the Modal Square of Opposition}. Studies in Universal Logic, Ed. B\'{e}ziau, J-Y. Springer. pp. 1--7.

@@

TODO: Check paper published in Logica Universalis 2016. 
TODO: 2013a lacks editors. Same for 2015b. 2015c.

% TODO: transform the following bibtex entries into bibitems

>>>>

\bibitem[{\itshape Benzm\"uller \& Weber \& Woltzenlogel Paleo(2017)}]{controversy}
Benzm\"uller, C. \& Weber, L. \& Woltzenlogel Paleo, B. 2017. {\itshape Computer-Assisted Analysis of the Anderson-H\'ajek Ontological Controversy}. To appear in: {\itshape Logica Universalis} Volume 11, Issue 1. Eds. Silvestre, R. S. \& B\'{e}ziau, J-Y. Springer. pp. 1--11.

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2013a)}]{IWIL}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2013a. {\itshape G{\"{o}}del's God on the Computer}. Proceedings of the 10th International Workshop on the Implementation of Logics. Eds. Schulz, S.; Sutcliffe, G. and Konev, B. pp. 1--2.

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015b)}]{ReasoningWebSummerSchool}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015b. {\itshape Higher-Order Modal Logics: Automation and Applications}. Reasoning Web. Web Logic Rules - 11th International Summer School 2015. Tutorial Lectures. Lecture Notes in Computer Science. Eds. Faber, W. and Paschke, A. Springer. pp. 32--74.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015c)}]{SpiritualQuest}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015c. {\itshape Experiments in Computational Metaphysics: G\"odel's Proof of God's Existence}. Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest. Vol. 9. Eds. Mishra, S.C.; Ghosh, S. and Agarwal, V. Bhaktivedanta Institute. pp. 23--40.

@@

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016b)}]{ModalCollapse}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016b. {\itshape The Modal Collapse as a Collapse of the Modal Square of Opposition}. Studies in Universal Logic. The Square of Opposition: A Cornerstone of Thought. Eds. B\'{e}ziau, J-Y. and Basti, G. Springer. pp. 1--7.

@@
